\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-18 tex/paper.tex
Fixed figures and added stack explanation

JPF was used to test the idea and state transitioning of the application. It's a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made in the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.

\subsubsection{Entities}
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

@@

\begin{figure}[htp] 
    \centering
    \includegraphics[scale=0.4]{reflux.png}
    \caption{Reflux unidirectional dataflow}
    \label{fig:reflux}
\end{figure}

@@

\begin{figure}[htp] \centering{
    \includegraphics[scale=0.4]{newtree.png}}
    \caption{Cloning mechanism of Btrfs~\cite{BTRFS}}
    \label{fig:btrfs_tree}
\end{figure}

@@

\fix Picture of the newest front-end
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.4]{frontend.png}}
    \caption{Front-end~\cite{BTRFS}}
    \label{fig:frontend}
\end{figure}

@@

\newpage
\section{Summary}
\subsection{Conclusions}
The goal of this thesis was to see whether it was feasible to use copy-on-write in a high level
application. As the implementation (see Section~\ref{sec:implementation}) made as a part of this 
thesis project is already replacing its predecessor the simple conclusion is that it definitely is 
possible. In the beginning of the project thoughts were on having every element being operated upon
in a copy-on-write fashion but this was later narrowed down to only have the most important part,
the files, as copy-on-write. This was due to that the conclusion that it did not matter if the 
other elements were resolved in a last-write-wins manner when modified.

>>>>

JPF was used to test the idea and state transitioning of the model. It's a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made in the model. This simplified version was then used to automatically
test for unwanted quirks. It is not a proof that the model works, but it is very exhaustive in its
testing.

\subsubsection{Entities}
\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.8]{relation.pdf}
    }
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

\begin{figure}[H] 
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|r|l|}
        \hline
        Application &
        \begin{tabular}{|r|l|}
            \hline
            Perius Front-end\\
            Perius Back-end\\
            \hline
        \end{tabular}\\
        Persistent Storage & MongoDB \\ \cline{2-2}
        Filesystem & Ext4 \\ \cline{2-2}
        OS & Arch Linux \\
        \hline \hline
        Hardware & \\
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Software Stack}
    \label{fig:stack}
\end{figure}

To clarify what is meant by Perius being high level software the stack in Figure~\ref{fig:stack} can
be examined. Theoretically the Copy-on-Write features could be implemented in any of the separate
parts of the stack to support the features that Perius has to achieve, in this work only the second
highest layer is considered, the Perius back-end.

@@

\begin{figure}[H] 
    \centering
    \includegraphics[scale=0.4]{reflux.png}
    \caption{Reflux unidirectional dataflow}
    \label{fig:reflux}
\end{figure}

@@

\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.4]{newtree.png}
    }
    \caption{Cloning mechanism of Btrfs~\cite{BTRFS}}
    \label{fig:btrfs_tree}
\end{figure}

@@

\fix Picture of the newest front-end
\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.4]{frontend.png}
    }
    \caption{Front-end~\cite{BTRFS}}
    \label{fig:frontend}
\end{figure}

@@

\newpage
\section{Summary}
\subsection{Conclusions}
The goal of this thesis was to see whether it was feasible to use copy-on-write in a high level
application (See Figure~\ref{fig:stack}). As the implementation (see
Section~\ref{sec:implementation}) made as a part of this thesis project is already replacing its
predecessor the simple conclusion is that it definitely is possible. In the beginning of the project
thoughts were on having every element being operated upon in a copy-on-write fashion but this was
later narrowed down to only have the most important part, the files, as copy-on-write. This was due
to that the conclusion that it did not matter if the other elements were resolved in a
last-write-wins manner when modified.
